Under-ice acoustic navigation using real-time model-aided range estimation

### 2022-02-21 manuscript/main.tex
GNSS instead of GPS on plot

\begin{figure}[h!]
	\centering
	\includegraphics[width=\reprintcolumnwidth]{figs/gps-drift-example.pdf} 
	\caption{A comparison of GPS drift (y-axis) versus OWTT drift (x-axis), colored by source and receiver depth.}
	\label{fig:gps-drift-example}
\end{figure}

>>>>

\begin{figure}[h!]
	\centering
	\includegraphics[width=\columnwidth]{figs/gps-drift-example.pdf} 
	\caption{A comparison of GPS drift (y-axis) versus OWTT drift (x-axis) for corners of the ICNN network with different source depths.}
	\label{fig:gps-drift-example}
\end{figure}
